
```{r}
library(tidyverse)
library(here)
library(janitor)
library(scales)
```

# Read in data, skipping 12 rows of introduction
```{r}
welfare <- read_csv(here("data/welfare_fund.csv"), skip = 8) %>% 
  clean_names()
```

# Pivot longer
```{r}
welfare <- welfare %>% 
  pivot_longer(cols = x2013_2014:x2019_2020,
               names_to = "year",
               names_prefix = "x",
               values_to = "expenditure")
```

# Visualise
```{r}
welfare %>% 
  filter(reference_area == "Scotland") %>% 
  ggplot() +
  aes(x = year, y = expenditure, group = reference_area, colour = reference_area) +
  geom_line() +
  geom_point() +
  labs(
    title = "Cost of crisis grants",
    x = "Year measured",
    y = "Expenditure"
  ) +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(labels = scales::comma)
```

Interesting to compare this with level of satisfaction with council. 3 distinct periods - 
2013-2015 increasing satisfaction, gradual increase crisis grant expenditure, 2015-2017: slow decline of council satisfaction, gradual increase crisis expenditure then decline.
2017-2019: rapid decline of council satisfaction, rapid increase in crisis grant expenditure.

Impact of austerity.
Who was in power.
Levels of inequality.
Edit year labels to end of year so we can match with other data sets.

